Figures and supplemental figures for ecological resilience ms

### 2024-01-05 ms_figures_supp_figs.qmd
Update readme instructions

biom_ts_plt <- facet_plot_bm_ts_plots(
  bio_yield_df = out_fs_brf_lp_mei,
  biomass_thresh = med_biomass_brf,
  yield_thresh = med_yield_brf,
  exp_deets = brf_lp_mei_nice,
  r_seed = 34,
  frac_reserves = c(0, 0.25, 0.50),
  f_fmsys = c(0, 0.5, 1.00, 2.)
)

yield_ts_plt <- facet_plot_yld_ts_plots(
  bio_yield_df = out_fs_brf_lp_mei,
  biomass_thresh = med_biomass_brf,
  yield_thresh = med_yield_brf,
  exp_deets = brf_lp_mei_nice,
  r_seed = 34,
  frac_reserves = c(0, 0.25, 0.50),
  f_fmsys = c(0.5, 1.00, 2.)
)

@@

frac_reserves <- c(0, 0.25, 0.5)
f_fmsys <- c(0, 0.5, 1.00, 2)

>>>>

biom_ts_plt <- facet_plot_bm_ts_plots(
  bio_yield_df = out_fs_brf_lp_mei,
  biomass_thresh = med_biomass_brf,
  yield_thresh = med_yield_brf,
  exp_deets = brf_lp_mei_nice,
  r_seed = 34,
  frac_reserves = c(0, 0.15, 0.30),
  f_fmsys = c(0, 0.5, 1.00, 2.)
)

yield_ts_plt <- facet_plot_yld_ts_plots(
  bio_yield_df = out_fs_brf_lp_mei,
  biomass_thresh = med_biomass_brf,
  yield_thresh = med_yield_brf,
  exp_deets = brf_lp_mei_nice,
  r_seed = 34,
  frac_reserves = c(0, 0.15, 0.30),
  f_fmsys = c(0.5, 1.00, 2.)
)

@@

frac_reserves <- c(0, 0.15, 0.3)
f_fmsys <- c(0, 0.5, 1.00, 2)
